---
title: "Traffic Dataset"
date: "11/18/2020"
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = T,
                      fig.show='hold',
                      results='hold')
#str(knitr::opts_chunk$get())
set.seed(25346534)

# https://r.789695.n4.nabble.com/Suppressing-output-e-g-from-cat-td859876.html
quiet <- function(x) { 
  sink(tempfile()) 
  on.exit(sink()) 
  invisible(force(x))
}

my.mse = function(pred,actual){
  if(length(pred) != length(actual)){
    stop("vectors arent same length")
  }
  
  return(mean((pred-actual)^2))
  
}

```


```{r libraries, message=F, echo=F}
library(astsa)

library(fracdiff)

library(tseries)

library(fGarch)

library(forecast)

library(ggplot2)

library(lubridate)

library(xts)

library(sarima)

library(Metrics)
```

# Input Data

```{r input-data,echo=F}
traffic.data = read.csv("./archive-iot/train_ML_IOT.csv")


#traffic.data$timeDatelt = as.POSIXlt(traffic.data$DateTime)

knitr::kable(head(traffic.data,10))

knitr::kable(tail(traffic.data,10))

traffic.1 = traffic.data[traffic.data$Junction == 1,]
traffic.2 = traffic.data[traffic.data$Junction == 2,]
traffic.3 = traffic.data[traffic.data$Junction == 3,]
traffic.4 = traffic.data[traffic.data$Junction == 4,]

traffic.1$Hour = (0:(nrow(traffic.1)-1)) %% 24
traffic.2$Hour = (0:(nrow(traffic.2)-1)) %% 24
traffic.3$Hour = (0:(nrow(traffic.3)-1)) %% 24
traffic.4$Hour = (0:(nrow(traffic.4)-1)) %% 24

traffic.1$Date = substr(as.character(traffic.1$DateTime),1,10)
traffic.2$Date = substr(as.character(traffic.2$DateTime),1,10)
traffic.3$Date = substr(as.character(traffic.3$DateTime),1,10)
traffic.4$Date = substr(as.character(traffic.4$DateTime),1,10)

traffic.1$Vehicles = ts(traffic.1$Vehicles, frequency = 7*24) # weekly frequency
traffic.2$Vehicles = ts(traffic.2$Vehicles, frequency = 7*24) # weekly frequency
traffic.3$Vehicles = ts(traffic.3$Vehicles, frequency = 7*24) # weekly frequency
traffic.4$Vehicles = ts(traffic.4$Vehicles, frequency = 7*24) # weekly frequency

cars = data.frame(Date = traffic.1$Date, Hour = traffic.1$Hour, junction1 = traffic.1$Vehicles, junction2 = traffic.2$Vehicles, junction3 = traffic.3$Vehicles)



cat("next")
```

\newpage


```{r}
knitr::kable(rbind(head(cars),tail(cars)))
cat("next")
```



```{r data-table}
# knitr::kable(head(traffic.data))
# knitr::kable(head(traffic.data[traffic.data$Junction == 2,]))
# knitr::kable(head(traffic.data[traffic.data$Junction == 3,]))
 knitr::kable(head(traffic.data[traffic.data$Junction == 4,1:3]))

knitr::kable(head(cbind(traffic.data[traffic.data$Junction == 1,1:3][1:10,],
       traffic.data[traffic.data$Junction == 2,2:3][1:10,],
       traffic.data[traffic.data$Junction == 3,2:3][1:10,])))

hold = cbind(traffic.data[traffic.data$Junction == 1,1:3],
             traffic.data[traffic.data$Junction == 2,2:3],
             traffic.data[traffic.data$Junction == 3,2:3])

cat("next")
```



# create daily cars


```{r}
dates = unique(cars$Date)
cars.day = data.frame(Date = dates, Junction1 = rep(NA,length(dates)), Junction2 = rep(NA,length(dates)), Junction3 = rep(NA,length(dates)))

for(i in 1:length(dates)){
  cars.day$Junction1[i] = sum(cars$junction1[cars$Date == dates[i]])
  cars.day$Junction2[i] = sum(cars$junction2[cars$Date == dates[i]])
  cars.day$Junction3[i] = sum(cars$junction3[cars$Date == dates[i]])
}

cars.day$Junction1 = ts(cars.day$Junction1, frequency = 7)
cars.day$Junction2 = ts(cars.day$Junction2, frequency = 7)
cars.day$Junction3 = ts(cars.day$Junction3, frequency = 7)

knitr::kable(rbind(head(cars.day),tail(cars.day)))

plot(cars.day$Junction1, type = "n", ylim = c(0,2250), main = "daily cars at junctions", xlab = "Time (day)", ylab = "cars")
grid()
lines(cars.day$Junction1, col = rainbow(3)[1])
lines(cars.day$Junction2, col = rainbow(3)[2])
lines(cars.day$Junction3, col = rainbow(3)[3])
legend("topleft",legend = c("Junction 1", "Junction 2", "Junction 3"), col = rainbow(3),lty = c(1,1,1))

plot(cars.day$Junction1, type = "n", ylim = c(0,2250), main = "daily cars at junctions 1 & 2", xlab = "Time (day)", ylab = "cars")
grid()
lines(cars.day$Junction1, col = rainbow(3)[1])
lines(cars.day$Junction2, col = rainbow(3)[2])
legend("topleft",legend = c("Junction 1", "Junction 2"), col = rainbow(3)[1:2],lty = c(1,1))
```


```{r}
acf(cars.day$Junction1, lag.max = 30, main = "Junction 1 ACF")
pacf(cars.day$Junction1, lag.max = 30, main = "Junction 1 PACF")

acf(cars.day$Junction2, lag.max = 30, main = "Junction 2 ACF")
pacf(cars.day$Junction2, lag.max = 30, main = "Junction 2 PACF")

acf(cars.day$Junction3, lag.max = 30, main = "Junction 3 ACF")
pacf(cars.day$Junction3, lag.max = 30, main = "Junction 3 PACF")
```


# create traning data

```{r}
# remove last month data

nday = nrow(cars.day)

cars.day.train = cars.day[-((nday-29):nday),] # remove last month

cars.day.train$Junction1 = ts(cars.day.train$Junction1,frequency = 7)
cars.day.train$Junction2 = ts(cars.day.train$Junction2,frequency = 7)
cars.day.train$Junction3 = ts(cars.day.train$Junction3,frequency = 7)

```


# auto arima

## Junction 1

```{r}
(cars.day.fit1 = auto.arima(cars.day.train$Junction1,
                           max.p = 5,
                        max.q = 5,
                        max.P = 5,
                        max.Q = 5,
                        max.order = 10,
                        max.d = 3,
                        max.D = 3,
                        start.p = 1,
                        start.q = 1,
                        start.P = 1,
                        start.Q = 1,
                        nmodels = 100,
                        approximation = T))


#quiet(astsa::sarima(cars.day.train$Junction1, p = 1, d = 1, q = 2))
```

## Junction 2

```{r}
(cars.day.fit2 = auto.arima(cars.day.train$Junction2,
                           max.p = 3,
                        max.q = 3,
                        max.P = 3,
                        max.Q = 3,
                        max.order = 5,
                        max.d = 1,
                        max.D = 1,
                        start.p = 1,
                        start.q = 1,
                        start.P = 1,
                        start.Q = 1,
                        nmodels = 100,
                        approximation = T))

quiet(astsa::sarima(cars.day.train$Junction2, p = 3, d = 1, q = 3))


```


## Junction 3

```{r}
(cars.day.fit3 = auto.arima(cars.day.train$Junction3,
                           max.p = 3,
                        max.q = 3,
                        max.P = 3,
                        max.Q = 3,
                        max.order = 5,
                        max.d = 1,
                        max.D = 1,
                        start.p = 2,
                        start.q = 2,
                        start.P = 2,
                        start.Q = 2,
                        nmodels = 50,
                        approximation = T))

quiet(astsa::sarima(cars.day.train$Junction1, p = 1, d = 1, q = 1))

```


# find seasonal model

## Junction 1

```{r}
cat("model 1")
(model1.1 = quiet(astsa::sarima(cars.day.train$Junction1, p = 1, d = 1, q = 2, P = 1, D = 0, Q = 0, S = 7)))
#AIC 6953.23

# model1.forecast2 = forecast(model1.1, h = 30)
# rmse1.1 = rmse(model1.forecast1$mean, data.1.full$J1[577:606])
# 114.3474


cat("model 2")
(model1.2 = quiet(astsa::sarima(cars.day.train$Junction1, p = 1, d = 1, q = 2, P = 0, D = 0, Q = 1, S = 7)))
#AIC 7297.4

cat("model 3")
(model1.3 = quiet(astsa::sarima(cars.day.train$Junction1, p = 1, d= 0, q = 1, P = 1, D = 1, Q = 0, S = 7)))
#AIC 6744.5

cat("model 4")
(model1.4 = quiet(astsa::sarima(cars.day.train$Junction1, p = 1, d= 1, q = 0, P = 2, D = 1, Q = 0, S = 7)))
#AIC 6749.55

cat("model 5")
(model1.5 = quiet(astsa::sarima(cars.day.train$Junction1, p = 1, d= 1, q = 0, P = 2, D = 0, Q = 0, S = 7)))
#AIC 6897.51


data.1 = data.frame(J1 = cars.day.train$Junction1[-c(1,2)],
                    J2L1 = cars.day.train$Junction2[-c(1,578)],
                    J2L2 = cars.day.train$Junction2[-c(577,578)],
                    J3L1 = cars.day.train$Junction3[-c(1,578)],
                    J3L2 = cars.day.train$Junction3[-c(577,578)])

data.1.full = data.frame(J1 = cars.day$Junction1[-c(1,2)],
                         J2L1 = cars.day$Junction2[-c(1,608)],
                         J2L2 = cars.day$Junction2[-c(607,608)],
                         J3L1 = cars.day$Junction3[-c(1,608)],
                         J3L2 = cars.day$Junction3[-c(607,608)])

cat("model 6")


# sarima(data.1$J1, p = 1, d= 1, q = 0, P = 2, D = 0, Q = 0, S = 7, 
#        xreg = cbind(data.1$J2L1,data.1$J3L1))

(model1.6 = quiet(astsa::sarima(data.1$J1, 
                              p = 1, 
                              d= 1, 
                              q = 0, 
                              P = 2, 
                              D = 0, 
                              Q = 0, 
                              S = 7, 
                              xreg = data.1[,-1])))

#AIC 6871.87

# model1.forecast1 = forecast(model1.6, h = 30)
# rmse1.1 = rmse(model1.forecast1$mean, data.1.full$J1[577:606])
# 114.3474

cat("model 7")
(model1.7 = quiet(astsa::sarima(data.1$J1, 
                              p = 1, 
                              d= 1, 
                              q = 1, 
                              P = 2, 
                              D = 0, 
                              Q = 0, 
                              S = 7, 
                              xreg = data.1[,-1])))

#AIC 6821.64

cat("model 8")
(model1.8 = quiet(astsa::sarima(data.1$J1, 
                              p = 2, 
                              d= 1, 
                              q = 1, 
                              P = 2, 
                              D = 0, 
                              Q = 0, 
                              S = 7, 
                              xreg = data.1[,-1])))

#AIC 6802.72

cat("model 9")
(model1.9 = quiet(astsa::sarima(data.1$J1, 
                              p = 2, 
                              d= 0, 
                              q = 1, 
                              P = 2, 
                              D = 1, 
                              Q = 0, 
                              S = 7, 
                              xreg = data.1[,-1])))

#AIC 6675.71

cat("model 10")
(model1.10 = quiet(astsa::sarima(data.1$J1, 
                              p = 2, 
                              d= 1, 
                              q = 1, 
                              P = 2, 
                              D = 1, 
                              Q = 0, 
                              S = 7, 
                              xreg = data.1[,-1])))

#AIC 6672.2

cat("model 11")
(model1.11 = quiet(astsa::sarima(data.1$J1, 
                              p = 3, 
                              d= 1, 
                              q = 1, 
                              P = 2, 
                              D = 1, 
                              Q = 0, 
                              S = 7, 
                              xreg = data.1[,-1])))

#AIC 6666.58

cat("model 12")
(model1.12 = quiet(astsa::sarima(data.1$J1, 
                              p = 2, 
                              d= 1, 
                              q = 3, 
                              P = 2, 
                              D = 1, 
                              Q = 0, 
                              S = 7, 
                              xreg = data.1[,-1])))

#AIC 6666.59

cat("model 13\n\n")
(model1.13<-Arima(data.1$J1, 
          order=c(1, 0, 1), 
          seasonal=list(order=c(0, 1, 1), period=7), 
          include.drift=T,
          xreg = as.matrix(data.1[,-1])))

model1.forecast1 = forecast(model1.13, h = 30, xreg = as.matrix(data.1.full[577:606,-1]))
rmse1.1 = rmse(model1.forecast1$mean, data.1.full$J1[577:606])
# 109.0436



#AIC 6610.41

cat("model 14n\n")
(model1.14<-Arima(data.1$J1, 
          order=c(1, 0, 1), 
          seasonal=list(order=c(0, 1, 1), period=7), 
          include.drift=T,
          xreg = as.matrix(data.1[,-c(1,3,4,5)])))

#AIC 6604.65


#plot(data.1$J2L1, data.1$J1)

```

$$
(1-0.822B)(1+0.82B^7)\nabla^{7}J_{1,t} = 1.906 +(1-0.401B)w_{1,t} + J_{2,t-1}
$$

## J1 model evaluation

```{r}
hist(model1.14$residuals, main = "histogram of residuals", freq = F, breaks = 35)
lines(-400:400,dnorm(-400:400, mean = mean(model1.14$residuals), sd = sd(model1.14$residuals)), col = "red")

plot(model1.14$residuals, main = "residual plot", type = "l")

adf.test(model1.14$residuals, alternative = "stationary")

acf(model1.14$residuals, main = "model 14 residual ACF")
pacf(model1.14$residuals, main = "model 14 residual PACF")


model1.forecast1 = forecast(cars.day.fit1, h = 30)
plot(model1.forecast1, xlim = c(75,90))
lines(cars.day$Junction1)


model1.forecast2 = forecast(model1.14, h = 30, xreg = data.1.full$J2L1[577:606])
plot(model1.forecast2, xlim = c(560,610))
lines(data.1.full$J1)

rmse1.1 = rmse(model1.forecast1$mean, data.1.full$J1[577:606])
# 114.3474

rmse1.2 = rmse(model1.forecast2$mean, data.1.full$J1[577:606])
# 109.6458

# mean(data.1.full$J1[577:606])
# 1761.767



```





## Junction 2

```{r}
#quiet(astsa::sarima(cars.day.train$Junction2, p = 3, d = 1, q = 3))

# ARIMA(2,0,1)(0,1,1)[7] with drift
# AIC 5435.15

data.2 = data.frame(J2 = cars.day.train$Junction2[-c(1,2)],
                    J1L1 = cars.day.train$Junction1[-c(1,578)],
                    J1L2 = cars.day.train$Junction1[-c(577,578)],
                    J3L1 = cars.day.train$Junction3[-c(1,578)],
                    J3L2 = cars.day.train$Junction3[-c(577,578)])

data.2.full = data.frame(J2 = cars.day$Junction2[-c(1,2)],
                         J1L1 = cars.day$Junction1[-c(1,608)],
                         J1L2 = cars.day$Junction1[-c(607,608)],
                         J3L1 = cars.day$Junction3[-c(1,608)],
                         J3L2 = cars.day$Junction3[-c(607,608)])



# (cars.day.fit2 = auto.arima(data.2$J2,
#                            max.p = 3,
#                         max.q = 3,
#                         max.P = 3,
#                         max.Q = 3,
#                         max.order = 5,
#                         max.d = 1,
#                         max.D = 1,
#                         start.p = 2,
#                         start.q = 1,
#                         start.P = 1,
#                         start.Q = 1,
#                         nmodels = 100,
#                         approximation = T, 
#                         seasonal = T))



(model2.1 = Arima(data.2$J2, 
          order=c(2, 0, 1), 
          seasonal=list(order=c(0, 1, 1), period=7), 
          include.drift=T,
          xreg = as.matrix(data.2[,-c(1)])))
#AIC 5415.31

(model2.2 = Arima(data.2$J2, 
          order=c(2, 0, 1), 
          seasonal=list(order=c(0, 1, 1), period=7), 
          include.drift=T,
          xreg = as.matrix(data.2[,-c(1,3)])))
#AIC 5413.33

(model2.3 = Arima(data.2$J2, 
          order=c(2, 0, 1), 
          seasonal=list(order=c(0, 1, 1), period=7), 
          include.drift=T,
          xreg = as.matrix(data.2[,-c(1,3,5)])))
#AIC 5411.81



```

## Junction 2 forecasts

```{r}

# ARIMA(2,0,1)(0,1,1)[7] with drift 
model2.forecast1 = forecast(cars.day.fit2, h = 30)
plot(model2.forecast1, xlim = c(75,90))
lines(cars.day$Junction2)
(rmse2.1 = rmse(model2.forecast1$mean, data.2.full[577:606,1]))
# 43.50
# AIC 5435.15

model2.forecast2 = forecast(model2.1, h = 30, 
                            xreg = as.matrix(data.2.full[577:606,-c(1)]))
plot(model2.forecast2, xlim = c(560,610))
lines(data.2.full$J2)
(rmse2.2 = rmse(model2.forecast2$mean, data.2.full[577:606,1]))
# 43.36

model2.forecast3 = forecast(model2.3, h = 30, 
                            xreg = as.matrix(data.2.full[577:606,-c(1,3,5)]))
plot(model2.forecast3, xlim = c(560,610))
lines(data.2.full$J2)
(rmse2.2 = rmse(model2.forecast3$mean, data.2.full[577:606,1]))
#42.88

```


## Junction 3

```{r}
#quiet(astsa::sarima(cars.day.train$Junction1, p = 1, d = 1, q = 1))

#ARIMA(1,1,1)(0,0,1)[7] 
# AIC 6878.07

data.3 = data.frame(J3 = cars.day.train$Junction3[-c(1,2)],
                    J1L1 = cars.day.train$Junction1[-c(1,578)],
                    J1L2 = cars.day.train$Junction1[-c(577,578)],
                    J2L1 = cars.day.train$Junction2[-c(1,578)],
                    J2L2 = cars.day.train$Junction2[-c(577,578)])

data.3.full = data.frame(J3 = cars.day$Junction3[-c(1,2)],
                         J1L1 = cars.day$Junction1[-c(1,608)],
                         J1L2 = cars.day$Junction1[-c(607,608)],
                         J2L1 = cars.day$Junction2[-c(1,608)],
                         J2L2 = cars.day$Junction2[-c(607,608)])


# cars.day.fit3
# ARIMA(1,1,1)(0,0,1)[7] 
# AIC=6878.07 


(model3.1 = Arima(data.3$J3, 
          order=c(1, 1, 1), 
          seasonal=list(order=c(0, 0, 1), period=7), 
          include.drift=T,
          xreg = as.matrix(data.3[,-c(1)]),
          method = "ML"))
#AIC 6857.59

(model3.2 = Arima(data.3$J3, 
          order=c(1, 1, 1), 
          seasonal=list(order=c(0, 0, 1), period=7), 
          include.drift=T,
          xreg = as.matrix(data.3[,-c(1,3,5)]),
          method = "ML"))
#AIC 6854.43

(model3.3 = Arima(data.3$J3, 
          order=c(1, 1, 1), 
          seasonal=list(order=c(0, 0, 1), period=7), 
          include.drift=T,
          xreg = as.matrix(data.3[,-c(1,2,3,5)]),
          method = "ML"))
#AIC 6853.18

(model3.4 = Arima(data.3$J3, 
          order=c(1, 1, 1), 
          seasonal=list(order=c(1, 0, 1), period=7), 
          include.drift=T,
          #xreg = as.matrix(data.3[,-c(1,2,3,5)]),
          method = "ML"))
#AIC 6842.05


```

## J3 forecasting

```{r}

model3.forecast1 = forecast(cars.day.fit3, h = 30)
plot(model3.forecast1, xlim = c(75,90))
lines(cars.day$Junction3)
(rmse3.1 = rmse(model3.forecast1$mean, data.3.full[577:606,1]))
# 124.8629


model3.forecast2 = forecast(model3.1, h = 30, 
                            xreg = as.matrix(data.3.full[577:606,-c(1)]))
plot(model3.forecast2, xlim = c(560,610))
lines(data.3.full$J3)
(rmse3.2 = rmse(model3.forecast2$mean, data.3.full[577:606,1]))
# 110.0729

model3.forecast3 = forecast(model3.4, h = 30)
plot(model3.forecast3, xlim = c(560,610))
lines(data.3.full$J3)
(rmse3.2 = rmse(model3.forecast3$mean, data.3.full[577:606,1]))
# 114.9068

```



# look at residuals for better fit

```{r resid-view}
#Hi
```



# TBATS
```{r TBATS}
fit <- tbats(data.1$J1, seasonal.periods = c(7))
fore = forecast(fit, h = 30)
plot(fore, xlim = c(75,90));
lines(ts(data.1.full$J1,frequency = 7))
# cat("model AIC is", fit$AIC) 
# AIC 8661.047
rmse.tbats = rmse(data.1.full$J1[577:606], fore$mean)
#148.5043
```

# Log fits

## J1 log

```{r}
(model1.log.1 = auto.arima(log(data.1$J1),
                           max.p = 5,
                        max.q = 5,
                        max.P = 5,
                        max.Q = 5,
                        max.order = 10,
                        max.d = 3,
                        max.D = 3,
                        start.p = 1,
                        start.q = 1,
                        start.P = 1,
                        start.Q = 1,
                        nmodels = 100,
                        approximation = T))

model1.log.forecast1 = forecast(model1.log.1, h = 30)
plot(model3.forecast3)
#, xlim = c(560,610)

lines(log(data.1.full$J1))
(rmse1.log.1 = rmse(model1.log.forecast1$mean, data.1.full[577:606,1]))
#1790.762
```



```{r}

cat("1\n\n\n\n")

auto.arima(cars.day.train$Junction1,
                           max.p = 5,
                           max.q = 5,
                           max.P = 5,
                           max.Q = 5,
                           max.order = 10,
                           max.d = 3,
                           max.D = 3,
                           start.p = 1,
                           start.q = 1,
                           start.P = 1,
                           start.Q = 1,
                           nmodels = 100,
                           approximation = T)

cat("\n\n2\n\n\n\n")

auto.arima(cars.day.train$Junction1[-c(1,2)],
                           max.p = 5,
                           max.q = 5,
                           max.P = 5,
                           max.Q = 5,
                           max.order = 10,
                           max.d = 3,
                           max.D = 3,
                           start.p = 1,
                           start.q = 1,
                           start.P = 1,
                           start.Q = 1,
                           nmodels = 100,
                           approximation = T)
```


```{r}
my.mat1 = matrix(0, nrow = 2, ncol = 3)
colnames(my.mat1) = c("Model 1", "Model 2", "Model 3")
rownames(my.mat1) = c("AIC","RMSE")

my.mat1[1,1] = 6631.91
my.mat1[1,2] = 6604.65
my.mat1[1,3] = 6608.14
my.mat1[2,1] = 114.34
my.mat1[2,2] = 109.64
my.mat1[2,3] = 115.10

knitr::kable(my.mat1)


my.mat2 = matrix(0, nrow = 2, ncol = 3)
colnames(my.mat2) = c("Model 1", "Model 2", "Model 3")
rownames(my.mat2) = c("AIC","RMSE")

my.mat2[1,1] = 5435.15
my.mat2[1,2] = 5415.31
my.mat2[1,3] = 5411.81
my.mat2[2,1] = 43.50
my.mat2[2,2] = 43.36
my.mat2[2,3] = 42.88

knitr::kable(my.mat2)



my.mat3 = matrix(0, nrow = 2, ncol = 3)
colnames(my.mat3) = c("Model 1", "Model 2", "Model 3")
rownames(my.mat3) = c("AIC","RMSE")

my.mat3[1,1] = 6878.07
my.mat3[1,2] = 6857.59
my.mat3[1,3] = 6842.05
my.mat3[2,1] = 124.86
my.mat3[2,2] = 110.07
my.mat3[2,3] = 114.90

knitr::kable(my.mat3)

```

note plot residuals for all models

# LateX

## Model 1

1

$$
(1-0.81B)(1+0.82B^7)(1-B^7)J_{1,t} = 2.12 + (1-0.34B)w_{1,t}
$$

```{r}
par(mfrow = c(2,2))

plot(cars.day.fit1$residuals, ylab = "residual", main = "residuals")
hist(cars.day.fit1$residuals, freq = F, xlab = "residuals", main = "residual histogram", breaks = 30)
lines(-600:600,dnorm(-600:600, mean = mean(cars.day.fit1$residuals), sd = sd(cars.day.fit1$residuals)), col = "red")
acf(cars.day.fit1$residuals, lag.max = 15, main = "residual ACF")
pacf(cars.day.fit1$residuals, lag.max = 15, main = "residual PACF")

```


2

$$
(1-0.822B)(1+0.82B^7)(1-B^7)J_{1,t} = 1.906 +(1-0.401B)w_{1,t} + 0.33J_{2,t-1}
$$

```{r}
par(mfrow = c(2,2))

plot(model1.14$residuals, ylab = "residual", main = "residuals")
hist(model1.14$residuals, freq = F, xlab = "residuals", main = "residual histogram", breaks = 30)
lines(-600:600,dnorm(-600:600, mean = mean(model1.14$residuals), sd = sd(model1.14$residuals)), col = "red")
acf(model1.14$residuals, lag.max = 15, main = "residual ACF")
pacf(model1.14$residuals, lag.max = 15, main = "residual PACF")

```

$$
1=2-1
$$

## Model 2

$$
(1-1.41B+0.43B^2)(1-B^7)J_{2,t} = 0.72 + (1-0.84B)(1-0.79B^7)w_{2,t}
$$

```{r}
par(mfrow = c(2,2))

plot(cars.day.fit2$residuals, ylab = "residual", main = "residuals")
hist(cars.day.fit2$residuals, freq = F, xlab = "residuals", main = "residual histogram", breaks = 30)
lines(-600:600,dnorm(-600:600, mean = mean(cars.day.fit2$residuals), sd = sd(cars.day.fit2$residuals)), col = "red")
acf(cars.day.fit2$residuals, lag.max = 15, main = "residual ACF")
pacf(cars.day.fit2$residuals, lag.max = 15, main = "residual PACF")

```

$$
(1-1.37B+0.39B^2)(1-B^7)J_{2,t} = 0.64 + (1-0.85B)(1-0.79B^7)w_{2,t} + 0.030J_{1,t-1} + 0.0019J_{1,t-2} + 0.026J_{3,t-1} + 0.0080J_{3,t-2}
$$

```{r}
par(mfrow = c(2,2))

plot(model2.1$residuals, ylab = "residual", main = "residuals")
hist(model2.1$residuals, freq = F, xlab = "residuals", main = "residual histogram", breaks = 30)
lines(-600:600,dnorm(-600:600, mean = mean(model2.1$residuals), sd = sd(model2.1$residuals)), col = "red")
acf(model2.1$residuals, lag.max = 15, main = "residual ACF")
pacf(model2.1$residuals, lag.max = 15, main = "residual PACF")

```

$$
(1-1.37B+0.39B^2)(1-B^7)J_{2,t} = 0.65 + (1-0.85B)(1-0.79B^7)w_{3,t} +0.029J_{1,t-1} 0.027J_{3,t-1}
$$

```{r}
par(mfrow = c(2,2))

plot(model2.3$residuals, ylab = "residual", main = "residuals")
hist(model2.3$residuals, freq = F, xlab = "residuals", main = "residual histogram", breaks = 30)
lines(-600:600,dnorm(-600:600, mean = mean(model2.3$residuals), sd = sd(model2.3$residuals)), col = "red")
acf(model2.3$residuals, lag.max = 15, main = "residual ACF")
pacf(model2.3$residuals, lag.max = 15, main = "residual PACF")

```


## Model 3

$$
(1-0.69B)\nabla J_{3,t} = (1-0.97B)(1+0.067B^7)w_{3,t}
$$

```{r}
par(mfrow = c(2,2))

plot(cars.day.fit3$residuals, ylab = "residual", main = "residuals")
hist(cars.day.fit3$residuals, freq = F, xlab = "residuals", main = "residual histogram", breaks = 30)
lines(-600:600,dnorm(-600:600, mean = mean(cars.day.fit3$residuals), sd = sd(cars.day.fit3$residuals)), col = "red")
acf(cars.day.fit3$residuals, lag.max = 15, main = "residual ACF")
pacf(cars.day.fit3$residuals, lag.max = 15, main = "residual PACF")

```

$$
(1-0.71B)\nabla J_{3,t} = 0.42+(1-1B)(1+0.065B^7)w_{3,t} -0.030J_{1,t-1} + 0.023J_{1,t-2} + 0.18J_{2,t-1} -0.10J_{2,t-2}
$$

```{r}
par(mfrow = c(2,2))

plot(model3.1$residuals, ylab = "residual", main = "residuals")
hist(model3.1$residuals, freq = F, xlab = "residuals", main = "residual histogram", breaks = 30)
lines(-600:600,dnorm(-600:600, mean = mean(model3.1$residuals), sd = sd(model3.1$residuals)), col = "red")
acf(model3.1$residuals, lag.max = 15, main = "residual ACF")
pacf(model3.1$residuals, lag.max = 15, main = "residual PACF")

```

$$
(1-0.73B)(1-0.99B^7)\nabla J_{3,t} = 0.45 + (1-B)(1-0.97B^7)w_{3,t}
$$

```{r}
par(mfrow = c(2,2))

plot(model3.4$residuals, ylab = "residual", main = "residuals")
hist(model3.4$residuals, freq = F, xlab = "residuals", main = "residual histogram", breaks = 30)
lines(-600:600,dnorm(-600:600, mean = mean(model3.4$residuals), sd = sd(model3.4$residuals)), col = "red")
acf(model3.4$residuals, lag.max = 15, main = "residual ACF")
pacf(model3.4$residuals, lag.max = 15, main = "residual PACF")

```



# Relationships between vars in the data.numbers

## J1

```{r}
par(mfrow = c(2,2))
plot(data.1.full$J2L1,data.1.full$J1, main = "J1 | J2(t-1)", xlab = "J2(t-1)", ylab = "J1")
abline(v = 450, col = "red", lty = 2)
plot(data.1.full$J2L2,data.1.full$J1, main = "J1 | J2(t-2)", xlab = "J2(t-2)", ylab = "J1")
abline(v = 450, col = "red", lty = 2)
plot(data.1.full$J3L1,data.1.full$J1, main = "J1 | J3(t-1)", xlab = "J3(t-1)", ylab = "J1")
plot(data.1.full$J3L2,data.1.full$J1, main = "J1 | J3(t-2)", xlab = "J3(t-2)", ylab = "J1")
```


```{r}
data.1.full2 = data.1.full

data.1.full2$J2L1L450 = ifelse(data.1.full$J2L1<450,data.1.full$J2L1,0)
data.1.full2$J2L1G450 = ifelse(data.1.full$J2L1>=450,1,0)
#data.1.full2$J2L1L4502 = ifelse(data.1.full$J2L1<450,data.1.full$J2L1,0)


data.1.2 = data.1.full2[-c(577:606),]

(model1.15 = Arima(data.1$J1, 
          order=c(1, 0, 1), 
          seasonal=list(order=c(0, 1, 1), period=7), 
          include.drift=T,
          xreg = as.matrix(data.1.2[,-c(1,2,3,4,5)])))

#AIC 6608.14

par(mfrow = c(2,2))
plot(model1.15$residuals, ylab = "residual", main = "residuals")
hist(model1.15$residuals, freq = F, xlab = "residuals", main = "residual histogram", breaks = 30)
lines(-600:600,dnorm(-600:600, mean = mean(model1.15$residuals), sd = sd(model1.15$residuals)), col = "red")
acf(model1.15$residuals, lag.max = 15, main = "residual ACF")
pacf(model1.15$residuals, lag.max = 15, main = "residual PACF")


par(mfrow = c(1,1))
model1.forecast3 = forecast(model1.15, h = 30, xreg = as.matrix(data.1.full2[577:606,-c(1:5)]))
plot(model1.forecast2, xlim = c(560,610))
lines(data.1.full$J1)

rmse1.3 = rmse(model1.forecast3$mean, data.1.full$J1[577:606])
#115.1091



```

$$
(1-0.80B)(1-B^7)J_{1,t} = 1.99+(1-0.36B)(1-0.81B^7)+ 0.32J_{2,t-1}(J_{2,t-1}<450) + 143.37(J_{2,t-1}\ge450)
$$


test $\mathbb{I}$  
$$
\mathbb{I}
$$


## J2

```{r}
par(mfrow = c(2,2))
plot(data.2.full$J1L1,data.2.full$J2, main = "J2 | J1(t-1)", xlab = "J1(t-1)", ylab = "J2")
plot(data.2.full$J1L2,data.2.full$J2, main = "J2 | J1(t-2)", xlab = "J1(t-2)", ylab = "J2")
plot(data.2.full$J3L1,data.2.full$J2, main = "J2 | J3(t-1)", xlab = "J3(t-1)", ylab = "J2")
plot(data.2.full$J3L2,data.2.full$J2, main = "J2 | J3(t-2)", xlab = "J3(t-2)", ylab = "J2")
```


## J3

```{r}
par(mfrow = c(2,2))
plot(data.3.full$J1L1,data.3.full$J3, main = "J3 | J1(t-1)", xlab = "J1(t-1)", ylab = "J3")
plot(data.3.full$J1L2,data.3.full$J3, main = "J3 | J1(t-2)", xlab = "J1(t-2)", ylab = "J3")
plot(data.3.full$J2L1,data.3.full$J3, main = "J3 | J2(t-1)", xlab = "J2(t-1)", ylab = "J3")
plot(data.3.full$J2L2,data.3.full$J3, main = "J3 | J2(t-2)", xlab = "J2(t-2)", ylab = "J3")
```




# residulal correlations

```{r}
# J1 model1.14
# J2 model2.3
# J3 model3.4

ggCcf(model1.14$residuals, model2.3$residuals)+ggtitle("CCF Plot for Junctions 1 & 2")
ggCcf(model1.14$residuals, model3.4$residuals)+ggtitle("CCF Plot for Junctions 1 & 3")
ggCcf(model2.3$residuals, model3.4$residuals)+ggtitle("CCF Plot for Junctions 2 & 3")
```

$$
(1-0.81B)(1-B^7)J_{1,t} = (1-0.34B)(1-0.82B^7)w_{1,t}
$$

$$
(1-0.82B)(1-B^7)J_{1,t} = 1.90+ (1-0.40B)(1-0.82B^7)w_{1,t} +0.33J_{2,t-1}
$$



```{r RAC, include=F}
#Hi
```

