---
title: "Power Study"
date: "3/20/2021"
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = T,
                      warning = F,
                      message = F,
                      fig.show='hold',
                      results='hold')
options(digits=3)
set.seed(1142646268)
```

# Libraries

```{r Libraries, message = F}
library(tidyverse)
library(readxl)
library(car)
library(MVN)
```

# Functions

```{r quiet}
# https://r.789695.n4.nabble.com/Suppressing-output-e-g-from-cat-td859876.html
quiet <- function(x) { 
  sink(tempfile())
  on.exit(sink())
  invisible(force(x))
}
```

```{r printMatrixAsLaTeX}
printMatrixAsLaTeX = function(A){
  #this function takes in a matrix input and will output a string that can 
  #be used to put a matrix into latex form
  m = nrow(A)
  #n = ncol(A)
  
  latex.list = list()
  
  for(i in 1:m){
    latex.list[[i]] = paste0(paste0(A[i,], collapse = " & "),"\\\\")
  }
  
  begin = "\\begin{bmatrix}"
  numbers = paste0(unlist(latex.list), collapse = "")
  end = "\\end{bmatrix}"
  str.out = paste0(begin, numbers, end, collapse = "")
  #cat(begin, numbers, end, sep = "")
  
  return(str.out)
}
```

$$
Odds = \frac{P}{1-P}
$$

```{r Odds}
Odds = function(p){
  return(p/(1-p))
}
```

```{r logOdds}
logOdds = function(p){
  return(log(p/(1-p)))
}
```



```{r Data}
period1 = read_excel("stock portfolio performance data set.xlsx", 
                     sheet = "1st period", skip = 1)
period2 = read_excel("stock portfolio performance data set.xlsx", 
                     sheet = "2nd period", skip = 1)
period3 = read_excel("stock portfolio performance data set.xlsx", 
                     sheet = "3rd period", skip = 1)
period4 = read_excel("stock portfolio performance data set.xlsx", 
                     sheet = "4th period", skip = 1)

allData = rbind(period1,period2,period3,period4) %>% select(-ID)
allData = allData[,c(1:6, 13:18)]
names(allData) = c(paste0("X",1:6), paste0("Y",1:6))
```

- X1 - Large B/P

- X2 - Large ROE

- X3 - Large S/P

- X4 - Large Return Rate in the last quarter

- X5 - Large Market Value

- X6 - Small systematic Risk

- Y1 - Annual Return

- Y2 - Excess Return

- Y3 - Systematic Risk

- Y4 - Total Risk

- Y5 - Abs. Win Rate

- Y6 - Rel. Win Rate


# Initial Histograms

```{r}
allData %>% ggplot(aes(x = Y1)) + 
  geom_histogram(aes(y = ..density..),color="black", fill="white") +
  geom_density() +
  labs(title = "Y1 - Annual Return") +
  theme_bw()
```




```{r}
allData %>% ggplot(aes(x = Y2)) + 
  geom_histogram(aes(y = ..density..),color="black", fill="white") +
  geom_density() +
  labs(title = "Y2 - Excess Return") +
  theme_bw()
```


```{r}
allData %>% ggplot(aes(x = Y3)) + 
  geom_histogram(aes(y = ..density..),color="black", fill="white") +
  geom_density() +
  labs(title = "Y3 - Systematic Risk") +
  theme_bw()
```

```{r}
allData %>% ggplot(aes(x = Y4)) + 
  geom_histogram(aes(y = ..density..),color="black", fill="white") +
  geom_density() +
  labs(title = "Y4 - Total Risk") +
  theme_bw()
```

```{r}
allData %>% ggplot(aes(x = Y5)) + 
  geom_histogram(aes(y = ..density..),color="black", fill="white") +
  geom_density() +
  labs(title = "Y5 - Abs. Win Rate ") + 
  theme_bw()
```

```{r}
allData %>% ggplot(aes(x = Y6)) + 
  geom_histogram(aes(y = ..density..),color="black", fill="white") +
  geom_density() +
  labs(title = "Y6 - Rel. Win Rate") +
  theme_bw()
```

# Odds transformation

```{r}
allData = allData %>% mutate(
  Z1 = Odds(Y1), 
  Z2 = Odds(Y2), 
  Z3 = Odds(Y3), 
  Z4 = Odds(Y4), 
)

Zdata = allData[,paste0("Z",1:4)]
p1 = powerTransform(Zdata$Z1)$start
p2 = powerTransform(Zdata$Z2)$start
p3 = powerTransform(Zdata$Z3)$start
p4 = powerTransform(Zdata$Z4)$start

pall = powerTransform(Zdata)

Zdata = Zdata %>% mutate(Z1 = Z1^0.232,
                            Z2 = Z2^0.267,
                            Z3 = Z3^-0.338,
                            Z4 = Z4^-0.418)

mvn(Zdata, mvnTest = "dh", multivariatePlot = "qq")

```

# Histograms of Z's

```{r}
Zdata %>% ggplot(aes(x = Z1)) + 
  geom_histogram(aes(y = ..density..),color="black", fill="white") +
  geom_density() +
  labs(title = "Z1 - Annual Return") + 
  theme_light()
```


```{r}
Zdata %>% ggplot(aes(x = Z2)) + 
  geom_histogram(aes(y = ..density..),color="black", fill="white") +
  geom_density() +
  labs(title = "Z2 - Excess Return") +
  theme_linedraw()
```


```{r}
Zdata %>% ggplot(aes(x = Z3)) + 
  geom_histogram(aes(y = ..density..),color="black", fill="white") +
  geom_density() +
  labs(title = "Z3 - Systematic Risk") +
  theme_linedraw()
```

```{r}
Zdata %>% ggplot(aes(x = Z4)) + 
  geom_histogram(aes(y = ..density..),color="black", fill="white") +
  geom_density() +
  labs(title = "Z4 - Total Risk") +
  theme_linedraw()
```






```{r fixZ4}
# hist(allData$`Annual Return...8`)

# df = allData$Y5 %>% as.tibble() %>% 
#   mutate(value2 = (value))
#   #mutate(value2 = log(beta(value,value)))
# 
# df %>% ggplot(aes(x = value2)) + 
#   geom_histogram(aes(y = ..density..),color="black", fill="white") +
#   geom_density(aes(x = value2)) +
#   stat_function(fun = dnorm,
#                 args = list(mean = mean(df$value2),
#                             sd = sd(df$value2)),
#                 col = "#1b98e0") +
#   labs(title = "Z5")

#shapiro.test(df$value2)
```

# Correlation plots

```{r corrplots}
library(corrplot)

initCor = cor(allData[,c(paste0("X",1:6), paste0("Y",1:4))])

col = colorRampPalette(c("red", "black", "blue"))(10)
corrplot(initCor, method = "number", type = "upper", col = col, bg="lightgray")
```

# Using updated data

```{r}
transformData = cbind(allData[paste0("X",1:6)], Zdata) %>% as.tibble()
```

```{r}
transformCor = cor(transformData)

col = colorRampPalette(c("red", "black", "blue"))(10)
corrplot(transformCor, method = "number", type = "upper", col = col, bg="lightgray")
```

# Initial Linear Models

```{r}
lm1 = lm(cbind(Z1,Z2,Z3,Z4) ~ (X1+X2+X3+X4+X5+X6)-1, 
          data = transformData)
summary(lm1)
```


```{r}
lm2 = lm(cbind(Z1,Z2,Z3,Z4) ~ (X1+X2+X3+X4+X5+X6)^2-1, 
          data = transformData)
summary(lm2)
```

```{r}
lm3 = lm(cbind(Z1,Z2,Z3,Z4) ~ (X1+X2+X3+X4+X5+X6)^3-1, 
          data = transformData)
summary(lm3)
```





# Bootstraps

```{r}
# for(i in 1:5){
#   for(j in (i+1):6){
#     cat("X",i,"X",j,"\n",sep = '')
#   }
# }

# for(i in 1:4){
#   for(j in (i+1):5){
#     for(k in (j+1):6){
#       cat("X",i,"X",j,"X",k," = ","X",i,"*X",j,"*X",k,",\n",sep = '')
#     }
#   }
# }

```

## LR1

this code is checking whether or not to keep 3rd order pairs

```{r LRratio1}
bootstrapData = transformData %>% mutate(
  X1X2 = X1*X2, X1X3 = X1*X3, X1X4 = X1*X4, X1X5 = X1*X5, X1X6 = X1*X6,
  X2X3 = X2*X3, X2X4 = X2*X4, X2X5 = X2*X5, X2X6 = X2*X6, X3X4 = X3*X4,
  X3X5 = X3*X5, X3X6 = X3*X6, X4X5 = X4*X5, X4X6 = X4*X6, X5X6 = X5*X6,
  X1X2X3 = X1*X2*X3, X1X2X4 = X1*X2*X4, X1X2X5 = X1*X2*X5,
  X1X2X6 = X1*X2*X6, X1X3X4 = X1*X3*X4, X1X3X5 = X1*X3*X5,
  X1X3X6 = X1*X3*X6, X1X4X5 = X1*X4*X5, X1X4X6 = X1*X4*X6,
  X1X5X6 = X1*X5*X6, X2X3X4 = X2*X3*X4, X2X3X5 = X2*X3*X5,
  X2X3X6 = X2*X3*X6, X2X4X5 = X2*X4*X5, X2X4X6 = X2*X4*X6,
  X2X5X6 = X2*X5*X6, X3X4X5 = X3*X4*X5, X3X4X6 = X3*X4*X6,
  X3X5X6 = X3*X5*X6, X4X5X6 = X4*X5*X6
)

n = nrow(bootstrapData)

Z = bootstrapData %>% select(Z1,Z2,Z3,Z4) %>% as.matrix()
m = ncol(Z) # number of responses

X = bootstrapData %>% select(-c(Z1,Z2,Z3,Z4)) %>% as.matrix()
r = ncol(X) # number of predictors (no constant involved)

b = solve(t(X) %*% X) %*% t(X) %*% Z
pred = X %*% b
resid = Z - pred


variables_to_test <- c(
  "X1X2X3",
  "X1X2X4",
  "X1X2X5",
  "X1X2X6",
  "X1X3X4",
  "X1X3X5",
  "X1X3X6",
  "X1X4X5",
  "X1X4X6",
  "X1X5X6",
  "X2X3X4",
  "X2X3X5",
  "X2X3X6",
  "X2X4X5",
  "X2X4X6",
  "X2X5X6",
  "X3X4X5",
  "X3X4X6",
  "X3X5X6",
  "X4X5X6"
)
variables_to_keep = setdiff(colnames(X), variables_to_test)
q = length(variables_to_keep)
grp1 = rownames(b) %in% variables_to_keep
grp2 = rownames(b) %in% variables_to_test

estSigma = t(resid) %*% resid / n

b_grp1 = solve(t(X[ , grp1]) %*% X[ , grp1]) %*% t(X[ , grp1]) %*% Z
pred_grp1 = X[ , grp1] %*% b_grp1
resid_grp1 = Z - pred_grp1

estSigma1 = t(resid_grp1) %*% resid_grp1 / n
LR_test_statistic = -n * (log(det(estSigma)) - log(det(estSigma1)))
# Approximate likelihood ratio test statistic:
approx_LR_test_statistic = 
  -(n - r - 1 - 0.5 * (m - r + q + 1)) * (log(det(estSigma)) - 
                                            log(det(estSigma1)))
cat("chiS1\n")
# Reject?
ifelse(approx_LR_test_statistic > qchisq(0.95, m * (r - q)), "Reject H0", "Don't reject H0")

# The corresponding p-value is:
pchisq(approx_LR_test_statistic, df = m * (r - q), lower.tail = FALSE)

cat("F stat\n")

# Or using the approximate F-statistic:
W <- det(estSigma) / det(estSigma1)

h <- length(variables_to_test)  
# h = q' = r - q; see corrected slide 25 in notes for Chapter 7

d1 <- (n - r - 1) - 0.5 * (m - h + 1)
d2 <- (m * h - 2)/4
d3 <- m^2 + h^2 - 5
d3 <- if (d3 > 0) { 
  sqrt(((m * h)^2 - 4) / d3)
} else { 1 }

F_approx_stat <- ((W^(-1 / d3) - 1) * (d1 * d3 - 2 * d2)) / (m  * h)

# The corresponding p-value is:
pf(F_approx_stat, m * h, d1 * d3 - 2 * d2, lower.tail = FALSE)

```

## check LR1 assumptions

```{r}
# Bootstrap study:
n <- nrow(bootstrapData)

S <- 500
LR_stat_sample <- numeric(S)

s <- 1
total = 0
while(s <= S){
  total = total+1
  try({
    bootstrap_sample_idx <- sample(n, replace = TRUE)
    bstp_df <- bootstrapData[bootstrap_sample_idx, ]
    
    Y <- bstp_df %>% select(Z1,Z2,Z3,Z4) %>% as.matrix()
    m <- ncol(Y)

    variables_to_test <- c(
      "X1X2X3",
      "X1X2X4",
      "X1X2X5",
      "X1X2X6",
      "X1X3X4",
      "X1X3X5",
      "X1X3X6",
      "X1X4X5",
      "X1X4X6",
      "X1X5X6",
      "X2X3X4",
      "X2X3X5",
      "X2X3X6",
      "X2X4X5",
      "X2X4X6",
      "X2X5X6",
      "X3X4X5",
      "X3X4X6",
      "X3X5X6",
      "X4X5X6"
    )
    
    variables_to_keep <- setdiff(colnames(Z), variables_to_test)
    grp1 <- rownames(b) %in% variables_to_keep
    grp2 <- rownames(b) %in% variables_to_test
    
    Z <- bootstrapData %>% select(-c(Z1,Z2,Z3,Z4)) %>% as.matrix()
    
    Z[ , grp2] <- Z[sample(n), grp2]   # shuffle rows of tested predictors
    
    r <- ncol(Z)
    
    b <- solve(t(Z) %*% Z) %*% t(Z) %*% Y
    pred <- Z %*% b
    resid <- Y - pred
    
    estSigma <- t(resid) %*% resid / n
    
    b_grp1 <- solve(t(Z[ , grp1]) %*% Z[ , grp1]) %*% t(Z[ , grp1]) %*% Y
    estSigma1 <- t(Y - Z[ , grp1] %*% b_grp1) %*% (Y - Z[ , grp1] %*% b_grp1) / n
    
    LR_stat_sample[s] <- det(estSigma) / det(estSigma1)
    s <- s + 1
    
  })
}

# p-value for bootstrap sample:
sum( LR_stat_sample < W ) / S
hist(LR_stat_sample)
abline(v = W)
```

```{r}
# Rescale the bootstrap sample to the approximate F scale:
h <- length(variables_to_test)
d1 <- (n - r - 1) - 0.5 * (m - h + 1)
d2 <- (m * h - 2)/4
d3 <- m^2 + h^2 - 5
d3 <- if (d3 > 0) { 
  sqrt(((m * h)^2 - 4) / d3)
} else { 1 }

F_approx_stat <- ((LR_stat_sample^(-1 / d3) - 1) * (d1 * d3 - 2 * d2)) / (m  * h)

crit_F <- ((W^(-1 / d3) - 1) * (d1 * d3 - 2 * d2)) / (m  * h)

hist(F_approx_stat, freq = FALSE, breaks = 40, main = "Bootstrap and F Approximation For 3rd Order")
rng <- range(F_approx_stat)
x <- seq(rng[1], rng[2], length.out = 100)
lines(x, df(x, m * h, d1 * d3 - 2 * d2))
abline(v = crit_F)
```


```{r}
# Rescale the bootstrap sample to the approximate chi squared scale:
chi_sq_approx_stat <- -(n - r - 1 - 0.5 * (m - r + q + 1)) * log(LR_stat_sample)

crit_chisq  <- -(n - r - 1 - 0.5 * (m - r + q + 1)) * log(W)

hist(chi_sq_approx_stat, freq = FALSE, breaks = 40, main = "Bootstrap and chi-square Approximation for 3rd Order")
rng <- range(chi_sq_approx_stat)
x <- seq(rng[1], rng[2], length.out = 100)
lines(x, dchisq(x, m * (r - q)))
abline(v = crit_chisq)
```


## LR2

This code is to check for certain 2nd order pairs

```{r LRratio2}
# bootstrapData = transformData %>% mutate(
#   X1X2 = X1*X2, X1X3 = X1*X3, X1X4 = X1*X4, X1X5 = X1*X5, X1X6 = X1*X6,
#   X2X3 = X2*X3, X2X4 = X2*X4, X2X5 = X2*X5, X2X6 = X2*X6, X3X4 = X3*X4,
#   X3X5 = X3*X5, X3X6 = X3*X6, X4X5 = X4*X5, X4X6 = X4*X6, X5X6 = X5*X6,
#   X1X2X3 = X1*X2*X3, X1X2X4 = X1*X2*X4, X1X2X5 = X1*X2*X5,
#   X1X2X6 = X1*X2*X6, X1X3X4 = X1*X3*X4, X1X3X5 = X1*X3*X5,
#   X1X3X6 = X1*X3*X6, X1X4X5 = X1*X4*X5, X1X4X6 = X1*X4*X6,
#   X1X5X6 = X1*X5*X6, X2X3X4 = X2*X3*X4, X2X3X5 = X2*X3*X5,
#   X2X3X6 = X2*X3*X6, X2X4X5 = X2*X4*X5, X2X4X6 = X2*X4*X6,
#   X2X5X6 = X2*X5*X6, X3X4X5 = X3*X4*X5, X3X4X6 = X3*X4*X6,
#   X3X5X6 = X3*X5*X6, X4X5X6 = X4*X5*X6
# )

bootstrapData = transformData %>% mutate(
  X1X2 = X1*X2, X1X3 = X1*X3, X1X4 = X1*X4, X1X5 = X1*X5, X1X6 = X1*X6,
  X2X3 = X2*X3, X2X4 = X2*X4, X2X5 = X2*X5, X2X6 = X2*X6, X3X4 = X3*X4,
  X3X5 = X3*X5, X3X6 = X3*X6, X4X5 = X4*X5, X4X6 = X4*X6, X5X6 = X5*X6
)

n = nrow(bootstrapData)

Z = bootstrapData %>% select(Z1,Z2,Z3,Z4) %>% as.matrix()
m = ncol(Z) # number of responses

X = bootstrapData %>% select(-c(Z1,Z2,Z3,Z4)) %>% as.matrix()
r = ncol(X) # number of predictors (no constant involved)

b = solve(t(X) %*% X) %*% t(X) %*% Z
pred = X %*% b
resid = Z - pred

variables_to_test = c(
  #"X1X2",#*
  "X1X3",
  #"X1X4",#*
  #"X1X5",#*
  #X1X6",#* **
  "X2X3",
  #"X2X4",#*
  "X2X5",
  #"X2X6",#*
  "X3X4",#*
  "X3X5",#*
  "X3X6",
  "X4X5",
  "X4X6",#*
  "X5X6"
)

variables_to_keep = setdiff(colnames(X), variables_to_test)
q = length(variables_to_keep)
grp1 = rownames(b) %in% variables_to_keep
grp2 = rownames(b) %in% variables_to_test

estSigma = t(resid) %*% resid / n

b_grp1 = solve(t(X[ , grp1]) %*% X[ , grp1]) %*% t(X[ , grp1]) %*% Z
pred_grp1 = X[ , grp1] %*% b_grp1
resid_grp1 = Z - pred_grp1

estSigma1 = t(resid_grp1) %*% resid_grp1 / n
LR_test_statistic = -n * (log(det(estSigma)) - log(det(estSigma1)))
# Approximate likelihood ratio test statistic:
approx_LR_test_statistic = 
  -(n - r - 1 - 0.5 * (m - r + q + 1)) * (log(det(estSigma)) - 
                                            log(det(estSigma1)))

# Reject?
ifelse(approx_LR_test_statistic > qchisq(0.95, m * (r - q)), "Reject H0", "Don't reject H0")

# The corresponding p-value is:
pchisq(approx_LR_test_statistic, df = m * (r - q), lower.tail = FALSE)


cat("F stat\n")

# Or using the approximate F-statistic:
W <- det(estSigma) / det(estSigma1)

h <- length(variables_to_test)  
# h = q' = r - q; see corrected slide 25 in notes for Chapter 7

d1 <- (n - r - 1) - 0.5 * (m - h + 1)
d2 <- (m * h - 2)/4
d3 <- m^2 + h^2 - 5
d3 <- if (d3 > 0) { 
  sqrt(((m * h)^2 - 4) / d3)
} else { 1 }

F_approx_stat <- ((W^(-1 / d3) - 1) * (d1 * d3 - 2 * d2)) / (m  * h)

# The corresponding p-value is:
pf(F_approx_stat, m * h, d1 * d3 - 2 * d2, lower.tail = FALSE)
```

## check LR2 assumptions

```{r}
# Bootstrap study:
n <- nrow(bootstrapData)

S <- 1000
LR_stat_sample <- numeric(S)

s <- 1
total = 0
while(s <= S){
  total = total+1
  try({
    bootstrap_sample_idx <- sample(n, replace = TRUE)
    bstp_df <- bootstrapData[bootstrap_sample_idx, ]
    
    Y <- bstp_df %>% select(Z1,Z2,Z3,Z4) %>% as.matrix()
    m <- ncol(Y)

    variables_to_test = c(
      #"X1X2",#*
      "X1X3",
      #"X1X4",#*
      #"X1X5",#*
      #X1X6",#* **
      "X2X3",
      #"X2X4",#*
      #"X2X5",
      #"X2X6",#*
      "X3X4",#*
      "X3X5",#*
      "X3X6",
      "X4X5",
      "X4X6",#*
      "X5X6"
    )
    
    variables_to_keep <- setdiff(colnames(Z), variables_to_test)
    grp1 <- rownames(b) %in% variables_to_keep
    grp2 <- rownames(b) %in% variables_to_test
    
    Z <- bootstrapData %>% select(-c(Z1,Z2,Z3,Z4)) %>% as.matrix()
    
    Z[ , grp2] <- Z[sample(n), grp2]   # shuffle rows of tested predictors
    
    r <- ncol(Z)
    
    b <- solve(t(Z) %*% Z) %*% t(Z) %*% Y
    pred <- Z %*% b
    resid <- Y - pred
    
    estSigma <- t(resid) %*% resid / n
    
    b_grp1 <- solve(t(Z[ , grp1]) %*% Z[ , grp1]) %*% t(Z[ , grp1]) %*% Y
    estSigma1 <- t(Y - Z[ , grp1] %*% b_grp1) %*% (Y - Z[ , grp1] %*% b_grp1) / n
    
    LR_stat_sample[s] <- det(estSigma) / det(estSigma1)
    s <- s + 1
    
  })
}

# p-value for bootstrap sample:
sum( LR_stat_sample < W ) / S
hist(LR_stat_sample, breaks = 30)
#abline(v = W)
```

```{r}
# Rescale the bootstrap sample to the approximate F scale:
h <- length(variables_to_test)
d1 <- (n - r - 1) - 0.5 * (m - h + 1)
d2 <- (m * h - 2)/4
d3 <- m^2 + h^2 - 5
d3 <- if (d3 > 0) { 
  sqrt(((m * h)^2 - 4) / d3)
} else { 1 }

F_approx_stat <- ((LR_stat_sample^(-1 / d3) - 1) * (d1 * d3 - 2 * d2)) / (m  * h)

crit_F <- ((W^(-1 / d3) - 1) * (d1 * d3 - 2 * d2)) / (m  * h)

hist(F_approx_stat, freq = FALSE, breaks = 40, main = "Bootstrap and F Approximation for 2nd Order Terms")
rng <- range(F_approx_stat)
x <- seq(rng[1], rng[2], length.out = 100)
lines(x, df(x, m * h, d1 * d3 - 2 * d2))
#abline(v = crit_F)
```


```{r}
# Rescale the bootstrap sample to the approximate chi squared scale:
chi_sq_approx_stat <- -(n - r - 1 - 0.5 * (m - r + q + 1)) * log(LR_stat_sample)

crit_chisq  <- -(n - r - 1 - 0.5 * (m - r + q + 1)) * log(W)

hist(chi_sq_approx_stat, freq = FALSE, breaks = 40, main = "Bootstrap and chi-square Approximation 2nd Order Terms")
rng <- range(chi_sq_approx_stat)
x <- seq(rng[1], rng[2], length.out = 100)
lines(x, dchisq(x, m * (r - q)))
#abline(v = crit_chisq)
```


# Final Model

```{r}
lm4 = lm(cbind(Z1,Z2,Z3,Z4) ~ (X1+X2+X3+X4+X5+X6) + X1:X2 + X1:X4 + X1:X5 + X1:X6 + X2:X4 + X2:X6 - 1, 
          data = transformData)
summary(lm4)
```





# test

```{r}
# b1 = 0.5
# b2 = 0.3
# b3 = 1.2
# b4 = 1.2
#   
# f1 = function(a){
#   return(b1*a + b2*(1-a))
# }
# 
# f2 = function(a){
#   return(b1*a + b2*(1-a) + b3*a*(1-a))
# }
# 
# x = seq(from = 0, to = 1, by = 0.01)
# 
# plot(x, f1(x), type = "l", col = "black", ylim = c(0, 1.5))
# lines(x, f2(x), col = "red")
```


```{r RAC, include=F}
# Hi
```

